A Constructive Ordered Predicate Logic for Category Theory

### 2022-10-13 paper/paper.tex
typos

%% orphaned --- move later? 
%% For any profunctor $R : \cat C \pto \cat D$ and functors $F : \cat C'
%% \to \cat C$ and $G : \cat D' \to \cat D$, by composition we can define a
%% profunctor $R(F,G)$, the ``restriction'' of $R$ along $F$ and $G$.
The remainder of this paper is organized as follows.  
In \cref{sec:syntax} we introduce the syntax of \vett{}.  In
\cref{sec:examples} we demonstrate how to use our syntax for formal
category theory.  In \cref{sec:semantics}, we develop some model theory
for \vett{}, including a sound and complete notion of categorical model
and sound interpretation in virtual equipments modeling ordinary,
enriched and internal category theory.  In \cref{sec:discussion}, we
discuss related type theories and potential extensions.

>>>>

%% orphaned --- move later? 
%% For any profunctor $R : \cat C \pto \cat D$ and functors $F : \cat C'
%% \to \cat C$ and $G : \cat D' \to \cat D$, by composition we can define a
%% profunctor $R(F,G)$, the ``restriction'' of $R$ along $F$ and $G$.
The remainder of this paper is organized as follows.  
In Section~\ref{sec:syntax} we introduce the syntax of \vett{}.  In
Section~\ref{sec:examples} we demonstrate how to use our syntax for formal
category theory.  In Section~\ref{sec:semantics}, we develop some model theory
for \vett{}, including a sound and complete notion of categorical model
and sound interpretation in virtual equipments modeling ordinary,
enriched and internal category theory.  In Section~\ref{sec:discussion}, we
discuss related type theories and potential extensions.
